Methodological details of the norming and production studies

### 2021-03-29 docs/methods_norm_prod/methods_norm_prod.Rmd
:memo: - edit RR (in prgoress)

---
title: "Methodological details of the norming and production studies"
author: ""
date: "9/17/2020"
output:
  bookdown::pdf_document2:
    number_sections: true
    keep_tex: true
fontsize: 12pt
header-includes:
  - \renewcommand{\familydefault}{\sfdefault}
  - \usepackage{expex}
  - \lingset{everygla=,everyglpreamble=\it}
  - \usepackage[export]{adjustbox}
---

@@

This document describes the methodological details of the norming study and the production study that generated the data your team will analyze for the *Many Speech Analyses* project.

>>>>

---
title: "Methodological details of the norming and production studies"
author: ""
output:
  bookdown::pdf_document2:
    number_sections: true
    keep_tex: true
fontsize: 12pt
header-includes:
  - \renewcommand{\familydefault}{\sfdefault}
  - \usepackage{expex}
  - \lingset{everygla=,everyglpreamble=\it}
  - \usepackage[export]{adjustbox}
---

@@

This document describes the methodological details of the norming and the production studies that generated the data your team will analyze for the *Many Speech Analyses* project.
